Fourmile Calibrations and Output

### 2023-05-05 38HRU_model/fourmile_model_outputs.Rmd
added rd and rg

<!-- ## RD and RG -->

<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->

<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'grid') -->

<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'statn') -->

<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
<!--   mutate(year = year(time)) %>% -->
<!--   rename(date = time) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- gw <- gw %>% -->
<!--   group_by(year, source) %>% -->
<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->

<!-- ################## -->
<!-- # all 4 with facets -->

<!-- ggplot(gw, aes(x=date)) + -->
<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
<!--   ggtitle('Cumulative RD and RG') + -->
<!--   theme(text = element_text(size = 24)) -->

<!-- ```{r gw boxplot, echo = F} -->

<!-- gw_maxcumsum <- gw %>% -->
<!--   group_by(source, year) %>% -->
<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
<!--             yr_max_RD2 = max(RD2cumsum), -->
<!--             yr_max_RG1 = max(RG1cumsum), -->
<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
<!--   mutate(year = as.factor(year)) %>% -->
<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ### RD and RG by season -->

<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->

<!-- #group by season and get max sums by season -->
<!-- flow_season <- gw %>% -->
<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
<!--   group_by(source, year, season) %>% -->
<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
<!--             yr_season_RD2 = max(RD2cumsum), -->
<!--             yr_season_RG1 = max(RG1cumsum), -->
<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(text = element_text(size = 20)) -->

>>>>

# RD and RG

```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}

gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid')

gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn')

gw <- bind_rows(gw_grid, gw_statn) %>%
  mutate(year = year(time)) %>%
  rename(date = time)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))

gw <- gw %>%
  group_by(year, source) %>%
  mutate(RD1cumsum = cumsum(catchmentRD1_w),
         RD2cumsum = cumsum(catchmentRD2_w),
         RG1cumsum = cumsum(catchmentRG1_w),
         RG2cumsum = cumsum(catchmentRG2_w))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2') +
  theme(text = element_text(size = 20))

```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}

##################
# all 4 with facets

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG') +
  theme(text = element_text(size = 24))

```{r gw boxplot, echo = F}

gw_maxcumsum <- gw %>%
  group_by(source, year) %>%
  summarize(yr_max_RD1 = max(RD1cumsum),
            yr_max_RD2 = max(RD2cumsum),
            yr_max_RG1 = max(RG1cumsum),
            yr_max_RG2 = max(RG2cumsum)) %>%
  mutate(year = as.factor(year)) %>%
  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Max annual cumulative sums')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Max annual cumulative sums')

### RD and RG by season

```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}

#group by season and get max sums by season
flow_season <- gw %>%
  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
  mutate(month = month(date)) %>%
  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
                            month %in% c(7,8,9,10) ~ 'monsoon',
                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
  group_by(source, year, season) %>%
  summarize(yr_season_RD1 = max(RD1cumsum),
            yr_season_RD2 = max(RD2cumsum),
            yr_season_RG1 = max(RG1cumsum),
            yr_season_RG2 = max(RG2cumsum)) %>%
            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size = 20))

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season + flow_type, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(text = element_text(size = 20))
